A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-15 pilot-publication/lab-book.Rmd
Add function that compares directly observed and retrospective data

## Keep only observations with any retrospective data
data <- data[apply(data[, retrospective.variables], 1, function(row) any(!is.na(row))), ] %>%
    as_tibble()

@@

## Change column classes to match original classes
merged.data[] <- mapply(function(column, class.name) {
    class.function <- paste0("as.", class.name[1])
    new.column <- match.fun(class.function)(column)
    return(new.column)
}, merged.data, original.classes, SIMPLIFY = FALSE)
})

## Create table 
table.variables <- c(
    "patinfo__pt_age", "patinfo__pt_gender",
    "incident__dominating_injury_type",
    "patvitals__ed_rr", "patvitals__ed_sat",
    "patvitals__ed_hr", "patvitals__ed_sbp","outcomes__alive_after_30_days", 
    "collection.mode"
)
table.data <- merged.data[, table.variables]
comparison.table <- create_descriptive_table(table.data,
    strata = "collection.mode")
```

>>>>

## Keep only observations with completed retrospective data collection
data <- data %>% filter(data_status_r__collection_completed_r == "Yes")

@@

## Change column classes to match original classes
merged.data[] <- mapply(function(column, class.name) {
    class.function <- paste0("as.", class.name[1])
    new.column <- match.fun(class.function)(column)
    return(new.column)
}, merged.data, original.classes, SIMPLIFY = FALSE)
merged.data <- merged.data %>%
    labelled::copy_labels_from(data)

## Create table
table.variables <- c(
    "patinfo__pt_age", "patinfo__pt_gender",
    "incident__dominating_injury_type",
    "patvitals__ed_rr", "patvitals__ed_sat",
    "patvitals__ed_hr", "patvitals__ed_sbp",
    "collection.mode"
)
table.data <- merged.data[, table.variables]
comparison.table <- create_descriptive_table(table.data,
    strata = "collection.mode",
    include.overall = FALSE
)
comparison.table
```
